MS_CNuptake.Rmd

### 2023-05-22 MS_CNuptake.Rmd
adjust space of unit

p1 <- analyse_modobs2(NPP_forest, "pred_npp","TNPP_1",type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", BP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest ", BP[pred.], " (gC m"^-2,"yr"^-1,")"))

p2 <- analyse_modobs2(NPP_forest,"pred_anpp", "ANPP_2",type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", ABP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest ", ABP[pred.], " (gC m"^-2,"yr"^-1,")"))

p3 <- analyse_modobs2(NPP_forest,"pred_lnpp","NPP.foliage", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest leaf ", BP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest leaf ", BP[pred.], " (gC m"^-2,"yr"^-1,")"))

p4 <- analyse_modobs2(NPP_forest, "pred_wnpp","NPP.wood",type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest wood ", BP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest wood ", BP[pred.], " (gC m"^-2,"yr"^-1,")"))

p5 <- analyse_modobs2(NPP_forest,"pred_bnpp","BNPP_1", type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", BBP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest ", BBP[pred.], " (gC m"^-2,"yr"^-1,")"))

p6 <- analyse_modobs2(NPP_forest,"pred_lnf","lnf_obs_final", type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest leaf N ", flux[obs.], " (gN m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest leaf N ", flux[pred.], " (gN m"^-2,"yr"^-1,")"))

p7 <- analyse_modobs2(NPP_forest,"pred_nuptake","Nmin", type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Net ", minerlization[obs.], " (gN m"^-2,"yr"^-1,")")) +labs(x = ~paste("Forest N ", uptake[pred.], " (gN m"^-2,"yr"^-1,")"))

@@

p8 <- analyse_modobs2(NPP_grassland,"grassland_pred_npp","TNPP_1", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", BP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Grassland ", BP[pred.], " (gC m"^-2,"yr"^-1,")"))

p9 <- analyse_modobs2(NPP_grassland,"grassland_pred_anpp","ANPP_2", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", ABP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Grassland ", ABP[pred.], " (gC m"^-2,"yr"^-1,")"))

p10 <- analyse_modobs2(NPP_grassland,"grassland_pred_bnpp","BNPP_1", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", BBP[obs.], " (gC m"^-2,"yr"^-1,")")) +labs(x = ~paste("Grassland ", BBP[pred.], " (gC m"^-2,"yr"^-1,")"))

@@

a4 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white+larger_plot_title

@@

a6 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white+larger_plot_title

@@

a12 <- gg$gglegend+labs(title = ~paste("gN m"^-2,"yr"^-1))+ white+larger_plot_title

@@

## Figure 3 without points
```{r}
#preparing one without showing points - in MS
total_value <- round(sum(all_maps[,"npp_pft"]*conversion,na.rm=TRUE),2)
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","npp_pft")]),
                varnam = "npp_pft",latmin = -65, latmax = 85,combine=FALSE)
a3 <- gg$ggmap +
  labs(title = paste("BP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title
a4 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white+larger_plot_title

#3.anpp
total_value <- round(sum(all_maps[,"anpp_pft"]*conversion,na.rm=TRUE),2)
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","anpp_pft")]),
                varnam = "anpp_pft",latmin = -65, latmax = 85,combine=FALSE)
a5 <- gg$ggmap +
  labs(title = paste("ABP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title
a6 <- gg$gglegend+labs(title = ~paste("gC m"^-2,"yr"^-1))+ white+larger_plot_title

@@

final1 <- ggplot() +xlim(8,30)+geom_line(data = subset(fits_tg,plt=="Measurement"), aes(Tg_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_tg, aes(Tg_a, visregFit, group=plt, color=plt),size=1) +theme_classic()+theme(text = element_text(size=20),legend.position="none")+  geom_ribbon(data = bp1a$fit,aes(Tg_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+labs(y = ~paste(BP, " (gC m"^-2,"yr"^-1,")"))+xlab("Tg (°C)")
final2 <- ggplot()+xlim(5.5,6.3)+geom_line(data = subset(fits_PPFD,plt=="Measurement"), aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")+geom_ribbon(data = bp1b$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+ scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab(~paste("ln gPPFD (", mu, "mol m"^-2,"s"^-1, ")"))
final3 <- ggplot()+xlim(-0.8,1) +geom_line(data = subset(fits_vpd,plt=="Measurement"), aes(vpd_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_vpd, aes(vpd_a, visregFit, group=plt, color=plt),size=1) + ylab(" ") +theme_classic()+theme(text = element_text(size=20),legend.position="none")+ geom_ribbon(data = bp1c$fit,aes(vpd_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab("ln D (kPa)")

@@

final1b <- ggplot()+xlim(8,30) + geom_line(data = subset(fits_tg,plt=="Measurement"),aes(Tg_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_tg, aes(Tg_a, visregFit, group=plt, color=plt),size=1) + 
  geom_ribbon(data=nn1b$fit,aes(Tg_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  xlab("Tg (°C)") +labs(y = ~paste("N uptake", " (gN m"^-2,"yr"^-1,")")) +
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+
  scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))

final1c <- ggplot()+xlim(5.5,6.3) +geom_line(data = subset(fits_ppfd,plt=="Measurement"),aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_ppfd, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + 
  geom_ribbon(data=nn1c$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  xlab(~paste("ln gPPFD (", mu, "mol m"^-2,"s"^-1, ")")) + ylab(" ")+
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+
  scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))

@@

final1_nue8 <- ggplot()+xlim(5.5,6.3) +geom_line(data = nue8c$fit, aes(PPFD_a, visregFit),size=4) +
  geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) +
  xlab(~paste("ln gPPFD (", mu, "mol m"^-2,"s"^-1, ")")) + ylab(" ")+
  geom_ribbon(data=nue8c$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))

>>>>

p1 <- analyse_modobs2(NPP_forest, "pred_npp","TNPP_1",type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", BP[obs.], " (g C m"^-2," yr"^-1,")")) +labs(x = ~paste("Forest ", BP[pred.], " (g C m"^-2," yr"^-1,")"))

p2 <- analyse_modobs2(NPP_forest,"pred_anpp", "ANPP_2",type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", ABP[obs.], " (g C m"^-2," yr"^-1,")")) +labs(x = ~paste("Forest ", ABP[pred.], " (g C m"^-2," yr"^-1,")"))

p3 <- analyse_modobs2(NPP_forest,"pred_lnpp","NPP.foliage", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest leaf ", BP[obs.], " (g C m"^-2," yr"^-1,")")) +labs(x = ~paste("Forest leaf ", BP[pred.], " (g C m"^-2," yr"^-1,")"))

p4 <- analyse_modobs2(NPP_forest, "pred_wnpp","NPP.wood",type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest wood ", BP[obs.], " (g C m"^-2," yr"^-1,")")) +labs(x = ~paste("Forest wood ", BP[pred.], " (g C m"^-2," yr"^-1,")"))

p5 <- analyse_modobs2(NPP_forest,"pred_bnpp","BNPP_1", type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest ", BBP[obs.], " (g C m"^-2," yr"^-1,")")) +labs(x = ~paste("Forest ", BBP[pred.], " (g C m"^-2," yr"^-1,")"))

p6 <- analyse_modobs2(NPP_forest,"pred_lnf","lnf_obs_final", type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Forest leaf N ", flux[obs.], " (g N m"^-2," yr"^-1,")")) +labs(x = ~paste("Forest leaf N ", flux[pred.], " (g N m"^-2," yr"^-1,")"))

p7 <- analyse_modobs2(NPP_forest,"pred_nuptake","Nmin", type = "points",relative=TRUE)$gg+ larger_size+coord_obs_pred()+
  labs(y = ~paste("Net ", minerlization[obs.], " (g N m"^-2," yr"^-1,")")) +labs(x = ~paste("Forest N ", uptake[pred.], " (g N m"^-2," yr"^-1,")"))

@@

p8 <- analyse_modobs2(NPP_grassland,"grassland_pred_npp","TNPP_1", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", BP[obs.], " (g C m"^-2," yr"^-1,")")) +labs(x = ~paste("Grassland ", BP[pred.], " (g C m"^-2," yr"^-1,")"))

p9 <- analyse_modobs2(NPP_grassland,"grassland_pred_anpp","ANPP_2", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", ABP[obs.], " (g C m"^-2," yr"^-1,")")) +labs(x = ~paste("Grassland ", ABP[pred.], " (g C m"^-2," yr"^-1,")"))

p10 <- analyse_modobs2(NPP_grassland,"grassland_pred_bnpp","BNPP_1", type = "points",relative=TRUE)$gg + larger_size+coord_obs_pred()+
  labs(y = ~paste("Grassland ", BBP[obs.], " (g C m"^-2," yr"^-1,")")) +labs(x = ~paste("Grassland ", BBP[pred.], " (g C m"^-2," yr"^-1,")"))

@@

a4 <- gg$gglegend+labs(title = ~paste("g C m"^-2," yr"^-1))+ white+larger_plot_title

@@

a6 <- gg$gglegend+labs(title = ~paste("g C m"^-2," yr"^-1))+ white+larger_plot_title

@@

a12 <- gg$gglegend+labs(title = ~paste("g N m"^-2," yr"^-1))+ white+larger_plot_title

@@

## Figure 3 without points
```{r}
#preparing one without showing points - in MS
total_value <- round(sum(all_maps[,"npp_pft"]*conversion,na.rm=TRUE),2)
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","npp_pft")]),
                varnam = "npp_pft",latmin = -65, latmax = 85,combine=FALSE)
a3 <- gg$ggmap +
  labs(title = paste("BP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title
a4 <- gg$gglegend+labs(title = ~paste("g C m"^-2," yr"^-1))+ white+larger_plot_title

#3.anpp
total_value <- round(sum(all_maps[,"anpp_pft"]*conversion,na.rm=TRUE),2)
gg <- plot_map3(na.omit(all_maps[,c("lon","lat","anpp_pft")]),
                varnam = "anpp_pft",latmin = -65, latmax = 85,combine=FALSE)
a5 <- gg$ggmap +
  labs(title = paste("ABP:", total_value, "PgC/yr", sep=" " ))+
  theme_grey(base_size = 12)+ white+larger_plot_title
a6 <- gg$gglegend+labs(title = ~paste("g C m"^-2," yr"^-1))+ white+larger_plot_title

@@

final1 <- ggplot() +xlim(8,30)+geom_line(data = subset(fits_tg,plt=="Measurement"), aes(Tg_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_tg, aes(Tg_a, visregFit, group=plt, color=plt),size=1) +theme_classic()+theme(text = element_text(size=20),legend.position="none")+  geom_ribbon(data = bp1a$fit,aes(Tg_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+labs(y = ~paste(BP, " (g C m"^-2," yr"^-1,")"))+xlab("Tg (°C)")
final2 <- ggplot()+xlim(5.5,6.3)+geom_line(data = subset(fits_PPFD,plt=="Measurement"), aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + ylab(" ")+theme_classic()+theme(text = element_text(size=20),legend.position="none")+geom_ribbon(data = bp1b$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+ scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab(~paste("ln gPPFD (", mu, "mol m"^-2," s"^-1, ")"))
final3 <- ggplot()+xlim(-0.8,1) +geom_line(data = subset(fits_vpd,plt=="Measurement"), aes(vpd_a, visregFit, group=plt, color=plt),size=4)+geom_line(data = fits_vpd, aes(vpd_a, visregFit, group=plt, color=plt),size=1) + ylab(" ") +theme_classic()+theme(text = element_text(size=20),legend.position="none")+ geom_ribbon(data = bp1c$fit,aes(vpd_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+scale_colour_manual(values=c(Measurement="black",CABLE="pink",ISAM="red",ISBA="#339999",JULES="#663399",LPJ="#0066CC",ORCHIDEE="#FF9933",ORCHICNP="cyan",SDGVM="yellow",CLASS="brown",CLM="darkgoldenrod",JSBACH="burlywood1",LPX="darkgreen"))+xlab("ln D (kPa)")

@@

final1b <- ggplot()+xlim(8,30) + geom_line(data = subset(fits_tg,plt=="Measurement"),aes(Tg_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_tg, aes(Tg_a, visregFit, group=plt, color=plt),size=1) + 
  geom_ribbon(data=nn1b$fit,aes(Tg_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  xlab("Tg (°C)") +labs(y = ~paste("N uptake", " (g N m"^-2," yr"^-1,")")) +
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+
  scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))

final1c <- ggplot()+xlim(5.5,6.3) +geom_line(data = subset(fits_ppfd,plt=="Measurement"),aes(PPFD_a, visregFit, group=plt, color=plt),size=4) +geom_line(data = fits_ppfd, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) + 
  geom_ribbon(data=nn1c$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  xlab(~paste("ln gPPFD (", mu, "mol m"^-2," s"^-1, ")")) + ylab(" ")+
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+
  scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))

@@

final1_nue8 <- ggplot()+xlim(5.5,6.3) +geom_line(data = nue8c$fit, aes(PPFD_a, visregFit),size=4) +
  geom_line(data = fits_PPFD, aes(PPFD_a, visregFit, group=plt, color=plt),size=1) +
  xlab(~paste("ln gPPFD (", mu, "mol m"^-2," s"^-1, ")")) + ylab(" ")+
  geom_ribbon(data=nue8c$fit,aes(PPFD_a, ymin=visregLwr, ymax=visregUpr),fill="gray",alpha=0.5)+
  theme_classic()+theme(text = element_text(size=20),legend.position="none")+scale_colour_manual(values=c(Measurement="black",ISAM="red",ORCHICNP="cyan",JSBACH="burlywood1",LPX="darkgreen"))
